---
title: "Cwong Assign11"
author: "Calvin Wong"
date: "4/13/2019"
output: html_document
---

Using the “cars” dataset in R, build a linear model for stopping distance 
as a function of speed and replicate the analysis of your textbook chapter 3 
(visualization, quality evaluation of the model, and residual analysis.)

```{r}
data(mtcars)
head(mtcars, 6)
```

I would like to test if mpg has any influence on qsec. I believe cars 
with a lower mpg have larger engines and therefore have better quarter-mile times.
Let's test this theory.

```{r}
qsecmpg <- lm(mtcars$qsec ~ mtcars$mpg)
plot(mtcars$qsec,mtcars$mpg)
abline(qsecmpg)
```

This linear model seems to fit my theory. Lets use regression to see if we can strengthen the case.

```{r}
summary(qsecmpg)
```

In this case, the y-intercept is a0 = 15.3548 and the slope is a1 = 0.1241.
Thus, the final regression model is:

qsec = 15.3548 + 0.1241 * mpg

For a good model, we typically would like to see a standard error that is at 
least five to ten times smaller than the corresponding coefficient.
For example, the standard error for mpg is 2.52 times smaller than
the coefficient value (0.12414/0.04916 = 2.52). This small ratio means that
there is high levels of variability in the slope estimate, a1. The standard
error for the intercept, a0, is 1.02978, which is roughly the same as the 
estimated value of 15.35477 for this coefficient. These values suggest
that the estimate of this coefficient for this model does not vary much.

The reported R2 of 0.1753 for this model means that the model only explains 
17.53 percent of the data’s variation. 

```{r}
plot(fitted(qsecmpg),resid(qsecmpg))
```

Overall, this plot tells us that using the mpg as the sole predictor in the 
regression model does not sufficiently or fully explain the data. There is 
no observable trend or pattern in the residuals.  

```{r}
qqnorm(resid(qsecmpg))
qqline(resid(qsecmpg))
```

The residuals seem to be normally distributed, the points plotted in this 
figure seem to follow the straight line well.