---
title: 'Cwong House Prices: Advanced Regression Techniques'
author: "Calvin Wong"
date: "5/26/2019"
output: html_document
---

```{r}
library(readr)
library(tidyverse)
library(corrplot)
library(pracma)
library(MASS)
library(gmodels)
library(tinytex)
```


```{r}
test <- read.csv('https://raw.githubusercontent.com/cwong79/DATA605/master/test.csv')
train <- read.csv('https://raw.githubusercontent.com/cwong79/DATA605/master/train.csv')
train.df <- data.frame(train)
```


##Modeling.  Build some type of multiple regression model and submit your model to the competition board.  Provide your complete model summary and results with analysis.  Report your Kaggle.com user name and score.

Lets look at numerical variables and see how they stack up against sale price. I wanted to pick variables with higher than .6 correlation and run it through a regression model to see how R values read. Due to the time constraint, I will only look at numerical values although I do realize the importance of categorical ones.

```{r}
numericVars <- which(sapply(train.df, is.numeric)) 
numericVarNames <- names(numericVars) 

all_numVar <- train.df[, numericVars] 
all_numVar <- all_numVar[ -c(1) ]
cor_numVar <- cor(all_numVar, use="pairwise.complete.obs") 

cor_sorted <- as.matrix(sort(cor_numVar[,'SalePrice'], decreasing = TRUE))
 
CorHigh <- names(which(apply(cor_sorted, 1, function(x) abs(x)>0.6)))
cor_numVar <- cor_numVar[CorHigh, CorHigh]
corrplot.mixed(cor_numVar, tl.col="black", tl.pos = "lt")
```

For building model I've removed the variables with less than 0.6 correlation to sale price. After that I've fitted a multiple regression model. A step wise regression to select best set of predictor variables. My model's R square value is at 0.7609. Since the p-value is less than 0.05 at a 5% significant level, we can surmice that the model is valid.

```{r}
model <- lm(SalePrice ~ ., data = all_numVar[CorHigh])
summary(model)
```

```{r}
pairs(~SalePrice+OverallQual+GrLivArea+GarageCars+GarageArea+TotalBsmtSF+X1stFlrSF,data=all_numVar,
      main="Scatterplot Matrix")
```

```{r}
test$SalePrice <- 0
 
test[] <- sapply(test, as.numeric)
myPred <- predict(model, newdata = test[, -51])

submit <- data.frame(Id = test$Id, SalePrice = myPred)
write.csv(submit, file = "SalePricePred.csv",  row.names = FALSE)
```

