---
title: "Discussion 11"
output:
  html_document:
  pdf_document: default
---

## Batter up 

We'll be looking at data from all 30 Major League Baseball teams and
examining the linear relationship between runs scored in a season and a number 
of other player statistics. Our aim will be to summarize these relationships 
both graphically and numerically in order to find which variable, if any, helps 
us best predict a team's runs scored in a season.

## The data

Let's load up the data for the 2011 season.

```{r load-data, eval=TRUE}
load("/Users/cwong79/Dropbox/Public/CUNY/DATA 605/more/mlb11.RData")
```

In addition to runs scored, there are seven traditionally used variables in the 
data set: at-bats, hits, home runs, batting average, strikeouts, stolen bases, 
and wins. There are also three newer variables: on-base percentage, slugging 
percentage, and on-base plus slugging. 

If the relationship looks linear, we can quantify the strength of the
relationship with the correlation coefficient. Here I am comparing runs versus at bats.

```{r cor, eval=TRUE}
cor(mlb11$runs, mlb11$at_bats)
```

Here is another comparison of runs versus hits.

```{r}
cor(mlb11$runs, mlb11$hits)
plot_ss(x = mlb11$hits, y = mlb11$runs)
```

The hits variable appears to predict runs better than at_bats since the r-squared value is higher and therefore the variability that can be explained by the model is higher.

runs ~ hits = 0.6419
runs ~ at_bats = 0.3729

```{r}
m2 <- lm(runs ~ hits, data = mlb11)
summary(m2)
```

Bat_avg has the highest R^2 value at 0.6561, therefore, best predicts runs.

```{r}
plot(mlb11$runs ~ mlb11$bat_avg)
m3 <- lm(runs ~ bat_avg, data = mlb11)
abline(m3)
summary(m3)
```

new_obs is the best predictor of runs with an R^2 value of 0.9349. The results does make sense because being on base and hitting a ball is a definitive criteria to make a run. 

```{r}
plot(mlb11$runs ~ mlb11$new_obs)
m4 <- lm(runs ~ new_obs, data = mlb11)
abline(m4)
summary(m4)
```

-   Check the model diagnostics for the regression model with the variable you 
    decided was the best predictor for runs.

```{r}
plot(m4$residuals ~ mlb11$new_obs)
abline(h = 0, lty = 3)
```

There seems to be constant variability as the points do not seem to follow any patterns.

```{r}
hist(m4$residuals)
```

The histogram of new_obs is nearly symmetrical and unimodal.

```{r}
qqnorm(m4$residuals)
qqline(m4$residuals)
```

The plot shows a very clear linear relationship.


