---
title: "Cwong Assign5"
author: "Calvin Wong"
date: "3/1/2019"
output: html_document
---

Choose independently two numbers B and C at random from the interval [0, 1] with uniform density. Prove that B and C are proper probability distributions.

Unfortunately, B and C are not properly distributed based on the heavy tails of the normal probability plots. In this instance, there are frequent outliers on both the low and the high end.

Note that the point (B,C) is then chosen at random in the unit square.

```{r}
library(ggpubr)
library(magrittr)

B <- runif(10000)
C <- runif(10000)

B_df<-as.data.frame(B)
C_df<-as.data.frame(C)

ggplot(B_df, aes(x=B)) + 
  geom_density() +
  labs(title = "Density Plot of B", x = "Random Values")

ggplot(C_df, aes(x=C)) + 
  geom_density() +
  labs(title = "Density Plot of C", x = "Random Values")

qqnorm(B, pch = 1, frame = FALSE)
qqline(B, col = "steelblue", lwd = 2)

qqnorm(C, pch = 1, frame = FALSE)
qqline(C, col = "steelblue", lwd = 2)
```

Let's calculate the probabilities anyways and see our results.

Find the probability that

(a) B + C < 1/2.
```{r}
sum((B+C) < .5)/10000
```

Here we add both values and determine the probability it will be less than .5 is 12.24%.

(b) BC < 1/2.
```{r}
sum((B*C) < .5)/10000
```

Here we sum both values and determine the probability it will be less than .5 is 84.59%.

(c) |B − C| < 1/2.
```{r}
sum(abs(B-C) < .5)/10000
```

Here we deduct B from C and determine the probability it will be less than .5 is 75.26%.

(d) max{B,C} < 1/2.
```{r}
max_cnt = 0
for(i in 1:length(B))
{
  if(max(c(B[i],C[i])) < 0.5)
  {
    max_cnt = max_cnt+1
  }
}
max_cnt/length(B)
```

Max of an ordered pair being less than .5 is 24.68%.

(e) min{B,C} < 1/2.
```{r}
min_cnt = 0
for(i in 1:length(B))
{
  if(min(c(B[i],C[i])) < 0.5)
  {
    min_cnt = min_cnt+1
  }
}
min_cnt/length(B)
```

Min of an ordered pair being less than .5 is 74.81%.